\documentclass[11pt,reqno]{amsart}

%==============================================================================
%  Two-sided bounds on the essential minimum of the Zhang--Zagier height
%
%  Compile with pdflatex (or xelatex). No non-standard packages required.
%==============================================================================

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage[round,authoryear]{natbib}   % author--year citations: \citet -> Author (year)
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage{url}
\usepackage{booktabs}

%------------------------------------------------------------------ theorems
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{remark}[theorem]{Remark}

%------------------------------------------------------------------ macros
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Qbar}{\overline{\Q}}
\newcommand{\hZ}{h_Z}
\newcommand{\Cee}{C_{82}}
\newcommand{\disc}{\operatorname{disc}}
\newcommand{\Res}{\operatorname{Res}}
\newcommand{\Li}{\operatorname{Li}}
\newcommand{\Cl}{\operatorname{Cl}}
\newcommand{\Ihat}{\widehat{I}}
\newcommand{\dnu}{\,d\nu}
\DeclareMathOperator{\Real}{Re}

\newcommand{\repo}{\url{https://github.com/tempcollab/optimizationproblems/tree/main/constants/82a}}
\newcommand{\repofile}[1]{\href{https://github.com/tempcollab/optimizationproblems/blob/main/constants/82a/certificate/#1}{\texttt{#1}}}

\begin{document}

\title[The Zhang--Zagier essential minimum and the energy method]
{An improved upper bound on the Zhang--Zagier essential minimum,\\
and an obstruction to the logarithmic-energy method on the lower side}

\author{Adib Hasan}
\address{SignalPilot AI}
\email{adib.hasan8@gmail.com}

\author{Akashnil Dutta}
\address{Incept Labs}

\author{Tarik Moon}
\address{SignalPilot AI}

\date{\today}

\subjclass[2020]{11R06, 11G50, 11Y40 (primary); 31A15 (secondary)}
\keywords{Zhang--Zagier height, essential minimum, Mahler measure, logarithmic
energy, discriminant, auxiliary functions, interval arithmetic}

\begin{abstract}
Let $\Cee$ denote the essential minimum of the Zhang--Zagier height
$\hZ(\alpha)=h(\alpha)+h(1-\alpha)$ on $\Qbar$. We prove the upper bound
\[
  \Cee \;\le\; 0.2540419719,
\]
improving the record $0.25443677$ of \citet{Doc01b} by enriching his
perturbed-polynomial limit-point family with two additional admissible
perturbing blocks; the bound is backed by an outward-rounded interval-arithmetic
certificate that the reader can re-run.

On the lower side, we examine whether the logarithmic-energy / discriminant
inequality of \citet{OSS}---the constraint behind the largest recent advance on
the Schur--Siegel--Smyth trace problem---can improve Flammang's $2018$ lower bound
$0.2487458$ \citep{F18}. We prove it cannot: the involution $z\mapsto1-z$ under
which $\hZ$ is symmetric forces every member of the balanced signed-sum moment
hierarchy $Q=\sum_i\varepsilon_i x_i$ ($\varepsilon_i\in\{\pm1\}$,
$\sum_i\varepsilon_i=0$) to be either symmetry-neutralized (the $2$-point energy)
or strictly slack at the optimal Flammang measure (every higher moment). The
mechanism is a closed-form \emph{spreading law}
$C_n(\mu)\approx\frac12\log\bigl(n\cdot\mathrm{Var}_\rho\bigr)$ that makes the
$2n$-point moment strictly positive for $n\ge2$ at every diffuse symmetric
measure. This explains, structurally, why the lower bound has resisted the modern
energy method. The certificates are available at \repo.
\end{abstract}

\maketitle

%==============================================================================
\section{Introduction}
%==============================================================================

For $\alpha\in\Qbar$ let $h(\alpha)$ be the absolute logarithmic Weil height. The
\emph{Zhang--Zagier height} is
\[
  \hZ(\alpha)\;=\;h(\alpha)+h(1-\alpha),
\]
a height that simultaneously measures the arithmetic complexity of $\alpha$ near
$0$ and near $1$. \citet{Zha95} and \citet{Zag93} initiated its study;
Zagier proved $\hZ(\alpha)\ge\tfrac12\log\frac{1+\sqrt5}{2}$ for
$\alpha\notin\{0,1,\tfrac{1\pm\sqrt{-3}}{2}\}$. The quantity of interest here is the
\emph{essential minimum}
\begin{equation}\label{eq:def}
  \Cee\;=\;\sup\Bigl\{\,H\in\R:\ \{\alpha\in\Qbar:\hZ(\alpha)\le H\}\ \text{is finite}\,\Bigr\},
\end{equation}
the largest height threshold below which only finitely many algebraic numbers
lie. Its exact value is unknown; the problem is to narrow the interval
$[\,\text{lower},\text{upper}\,]$ bracketing it.

The two sides are approached by dual methods. Lower bounds come from Smyth's
auxiliary-function method \citep{S80}, developed for $\hZ$ by \citet{Doc01a}
and \citet{F18}, whose bound $\Cee\ge\log 1.282416=0.2487458$ has stood
since. Upper bounds come from explicit limit-point constructions;
\citet{Doc01b} gives $\Cee\le\log 1.289735=0.25443677$.
\citet{BMQS} recently proved that these two
methods are linear-programming duals of one another, with \emph{no duality gap},
so the residual interval reflects only how far the two finite optimizations have
been pushed.

This paper has two results, one positive and one negative.

\begin{theorem}[Upper bound]\label{thm:upper-intro}
$\Cee\le 0.2540419719$, strictly improving the Doche record $0.25443677$.
\end{theorem}

\begin{theorem}[Lower-side obstruction]\label{thm:nogo-intro}
Let $\mu$ be a $z\mapsto1-z$ invariant probability measure of finite logarithmic
energy on the Zhang--Zagier contour, and let $n\ge2$. Then the $2n$-point balanced
signed-sum moment satisfies $C_n(\mu)\ge0$; at the optimal Flammang measure the
inequality is strict, $C_n\ge0.36$. Consequently no member of the balanced
signed-sum moment hierarchy beyond the $2$-point energy supplies a dual column
that improves Flammang's lower bound, and the $2$-point energy is itself
neutralized by the symmetry. The phenomenon is governed by the spreading law of
Section~\ref{sec:nogo}.
\end{theorem}

Theorem~\ref{thm:upper-intro} (proved as Theorem~\ref{thm:upper} in
Section~\ref{sec:upperproof}) is a rigorous, certificate-backed improvement of the
Doche record. Theorem~\ref{thm:nogo-intro} (Theorem~\ref{thm:nogo} in
Section~\ref{sec:nogo}) explains why the lower bound has been hard to move: the
\emph{logarithmic-energy / discriminant inequality} of \citet{OSS}---the
constraint that produced the largest advance on the Schur--Siegel--Smyth trace
problem in forty years---is the natural tool to enrich Flammang's
auxiliary-function method, yet the $z\mapsto1-z$ symmetry of $\hZ$ blocks it and
its entire moment hierarchy. The trace problem lives on the real line, where the
energy column is decisive; the Zhang--Zagier conjugates lie on a symmetric complex
contour, and that symmetry is exactly what drains the energy constraint of its
power. To our knowledge this is the first analysis of the energy method for the
Zhang--Zagier essential minimum.

\medskip
\noindent\textbf{On rigor and reproducibility.}
The upper bound is certified by \emph{outward-rounded interval arithmetic}: each
floating-point operation in the verifying program is replaced by a guaranteed
enclosure (directed rounding via \texttt{numpy.nextafter}), so the bound does not
depend on an unrounded float. The obstruction of Section~\ref{sec:nogo} is proved
at the level of measures and corroborated by direct computation of the moments
$C_n$. The programs and a one-line reproduction command for the upper bound are
collected in Section~\ref{sec:repro} and hosted at \repo.

%==============================================================================
\section{Setup and notation}\label{sec:setup}
%==============================================================================

If $\alpha$ is an algebraic integer of degree $d$ with conjugates
$\alpha_1,\dots,\alpha_d$ and minimal polynomial $P\in\Z[z]$, then
\[
  \hZ(\alpha)\;=\;\tfrac1d\log Z(\alpha),\qquad
  Z(\alpha)\;=\;M(\alpha)\,M(1-\alpha),
\]
with $M$ the Mahler measure; we also write $\zeta(\alpha)=Z(\alpha)^{1/d}$, so
$\hZ(\alpha)=\log\zeta(\alpha)$.

We work in the symmetric coordinate
\[
  w\;=\;z(1-z),
\]
invariant under $z\mapsto 1-z$. On the unit circle $z=e^{it}$ we set
$w(t)=e^{it}-e^{2it}$, $t\in[0,\pi]$. The Zhang--Zagier Green function is
\[
  g(z)\;=\;\log^+|z|+\log^+|1-z|,\qquad \log^+x=\log\max(1,x),
\]
and on $|z|=1$ one has $g|_{\{|z|=1\}}=\log^+|w(t)|$.

For an algebraic integer $\alpha\notin\{0,1\}$ of degree $d$ the \emph{conjugate
measure} is $\nu=\frac1d\sum_{i=1}^d\delta_{\alpha_i}$ (in the $z$-coordinate);
since $P\in\Z[z]$, $\nu$ is invariant under complex conjugation.

We use the duality of \citep[Thm.~6.5]{BMQS}: with $g$ as above,
\[
  \underbrace{D(g)}_{\text{auxiliary-function (lower)}}
  \;=\;\Cee\;=\;
  \underbrace{P(g)}_{\text{measure (upper)}},
\]
strong duality with no gap. Here $D(g)$ is the supremum over $c_j\ge0$,
$Q_j\in\Z[x]\setminus\{0\}$ of $\inf_z\bigl(g(z)-\sum_jc_j\log|Q_j(z)|\bigr)$, and
$P(g)$ is the infimum of $\int g\,d\mu$ over conjugation-invariant probability
measures $\mu$ with $\int\log|Q|\,d\mu\ge0$ for all $Q\in\Z[x]\setminus\{0\}$.

\medskip
\noindent\textbf{The reference bounds.}
The best previously \emph{verified} bounds are the Flammang lower bound
$0.2487458=\log 1.282416$ \citep{F18} and the Doche upper bound
$0.25443677=\log1.289735$ \citep{Doc01b}. (The structural paper \citep{BMQS} quotes
the weaker pair $0.248247\le\Cee\le0.254437$ and does not cite Flammang; the
genuine bar is the Flammang/Doche pair.) We improve the upper bound
(Section~\ref{sec:upperproof}) and prove an obstruction to improving the lower
bound by the energy method (Section~\ref{sec:nogo}).

%==============================================================================
\section{The auxiliary-function method and the integrality columns}\label{sec:aux}
%==============================================================================

We recall Smyth's method as used by Flammang, isolating the load-bearing
integrality step, because the new energy column of Section~\ref{sec:energy} rests
on the same step.

Fix weights $c_j\ge0$ and integer polynomials $Q_j\in\Z[w]$, $1\le j\le J$, a real
$\lambda_0\ge0$, and a nonnegative \emph{energy column} $E(z)\ge0$ to be defined in
Section~\ref{sec:energy} (set $\lambda_0=0$ for the classical method). Consider
\begin{equation}\label{eq:aux}
  f(z)\;=\;g(z)\;-\;\sum_{j=1}^{J}c_j\log|Q_j(w)|\;-\;\lambda_0\,E(z),
  \qquad w=z(1-z).
\end{equation}

\begin{proposition}[Drop-out]\label{prop:dropout}
Let $\alpha$ be an algebraic integer of degree $d$ whose minimal polynomial $P$
divides none of the polynomials $Q_j(z(1-z))$, and suppose the energy column
satisfies $\int E\dnu\ge0$. If $f(z)\ge m$ for all $z$ with $|z|=1$, then
$\hZ(\alpha)\ge m$.
\end{proposition}

\begin{proof}
Average \eqref{eq:aux} against the conjugate measure $\nu$. By definition
$\int g\dnu=\frac1d\log Z(\alpha)=\hZ(\alpha)$. For each column,
\[
  \int\log|Q_j(w)|\dnu
  =\tfrac1d\log\Bigl|\textstyle\prod_{i=1}^d Q_j\bigl(\alpha_i(1-\alpha_i)\bigr)\Bigr|
  =\tfrac1d\log\bigl|\Res\bigl(P(z),Q_j(z(1-z))\bigr)\bigr|.
\]
The resultant is the determinant of an integer Sylvester matrix, hence an integer;
it is nonzero precisely because $P\nmid Q_j(z(1-z))$. Thus $|\Res|\ge1$ and
\begin{equation}\label{eq:colpos}
  \int\log|Q_j(w)|\dnu\;\ge\;0 .
\end{equation}
With $c_j\ge0$ these terms are subtracted with nonnegative weight, and likewise
$\lambda_0\ge0$, $\int E\dnu\ge0$. Hence
\[
  \hZ(\alpha)=\int g\dnu\;\ge\;\int f\dnu\;\ge\;m. \qedhere
\]
\end{proof}

\paragraph{The finite exception set}
Proposition~\ref{prop:dropout} fails only for the finitely many $\alpha$ that are
roots of some fixed nonzero $Q_j(z(1-z))$; the energy column of
Section~\ref{sec:energy} contributes no exceptions, since
$I(\nu)\ge0$ holds for every minimal polynomial (Proposition~\ref{prop:energy}).
Let $E_{\mathrm{exc}}=\bigcup_j\{\,\alpha:Q_j(\alpha(1-\alpha))=0\,\}$ be the
finite union of these root sets; then $\hZ(\alpha)\ge m$ for all algebraic
integers $\alpha\notin E_{\mathrm{exc}}$.

\paragraph{A finite exception set does not lower \texorpdfstring{$\Cee$}{C82}}
If $\hZ(\alpha)\ge m$ for all $\alpha\notin E_{\mathrm{exc}}$ with
$E_{\mathrm{exc}}$ finite, then for every $H<m$ the sublevel set
$\{\alpha:\hZ(\alpha)\le H\}\subseteq E_{\mathrm{exc}}$ is finite, so every $H<m$
is admissible in \eqref{eq:def} and $\Cee\ge m$. The restriction to algebraic
integers is harmless: for non-integers the leading coefficient only raises $h$.

\paragraph{Reduction to the unit circle (Flammang's baseline)}
For the classical method ($\lambda_0=0$) the function $f=g-\sum_jc_j\log|Q_j|$ is
superharmonic off the zeros of the $Q_j$ and symmetric under $z\mapsto1-z$ (both $g$
and each $\log|Q_j(w)|$ depend on $z$ only through $w$), so by the minimum principle
its infimum over $\C$ is attained on $\{|z|=1\}$, where $z=e^{it}$ and
\begin{equation}\label{eq:f-circle}
  f|_{\{|z|=1\}}(t)=\log^+|w(t)|-\sum_jc_j\log|Q_j(w(t))|,\qquad t\in[0,\pi].
\end{equation}
With Flammang's $J=24$ Table~1 columns the rigorous minimum of \eqref{eq:f-circle} is
$\ge0.2487458$; we re-certified this from scratch by outward-rounded interval
branch-and-bound (\repofile{verify\_vec.py}, cross-checked by the scalar
\repofile{verify\_flammang.py}), independently re-deriving \eqref{eq:colpos}. This is
the bound the energy method of the next sections aims, and fails, to improve.

\medskip\noindent\textbf{Why the symmetry is load-bearing.} The reduction
\eqref{eq:f-circle} uses $f(z)=f(1-z)$ in an essential way: it is what collapses the
two circles $\{|z|=1\}$ and $\{|1-z|=1\}$, on \emph{both} of which conjugates of a
small-$\hZ$ integer concentrate, to a single one-dimensional minimization. An added
term that breaks this symmetry would have to be controlled on both circles
separately. We return to this point in Section~\ref{sec:nogo}; it is the crux of the
obstruction.

%==============================================================================
\section{The logarithmic-energy column}\label{sec:energy}
%==============================================================================

The natural way to push the lower bound past Flammang is to adjoin a dual column her
method does not carry. The candidate, transferred from the trace problem, is the
logarithmic-energy / discriminant constraint of \citet{OSS}. We record it precisely
(it is a valid construction), and then show in Section~\ref{sec:nogo} that the
$z\mapsto1-z$ symmetry of $\hZ$ blocks it and its entire moment hierarchy.

\subsection{The energy constraint}
Let $\alpha$ be an algebraic number of degree $d$ with minimal polynomial $P\in\Z[z]$
and conjugate measure $\nu$. The \emph{logarithmic energy} of $\nu$ is
\begin{equation}\label{eq:Inu}
  I(\nu):=\iint\log|z_1-z_2|\,d\nu(z_1)\,d\nu(z_2)=\frac1{d^2}\log\bigl|\disc(P)\bigr|.
\end{equation}
The minimal polynomial of an algebraic number is irreducible over $\Q$, hence
separable in characteristic $0$, so $\disc(P)\neq0$; being the determinant of an
integer matrix it is a nonzero integer, so $|\disc(P)|\ge1$ and
\begin{equation}\label{eq:Ipos}
  I(\nu)\;\ge\;0\qquad\text{for every algebraic number }\alpha,
\end{equation}
with \emph{no} exception set. This is the instance $Q(z_1,z_2)=z_1-z_2$ of the
multivariate integrality $\int\!\cdots\!\int\log|Q|\,d\nu\cdots d\nu\ge0$,
$Q\in\Z[z_1,\dots,z_n]$ \citep{OSS,OT23}, and is independent of the univariate
columns \eqref{eq:colpos}.

\subsection{Linearization}
Constraint \eqref{eq:Ipos} is quadratic in $\nu$, so it cannot enter the linear
auxiliary function \eqref{eq:aux} directly. Following \citet[eq.~(8)]{OSS} we linearize
it, using the negative-definiteness of the logarithmic kernel.

\begin{lemma}[Ahlfors; {\citealp[Lem.~2.1]{Ahl10}}, {\citealp[eq.~(6)]{OSS}}]
\label{lem:nsd}
For any two compactly supported probability measures $\nu,\mu_0$ on $\C$ of finite
logarithmic energy,
\begin{equation}\label{eq:nsd}
  I(\nu)+I(\mu_0)-2I(\nu,\mu_0)\;\le\;0,\qquad
  I(\nu,\mu_0):=\iint\log|z_1-z_2|\,d\nu(z_1)\,d\mu_0(z_2).
\end{equation}
\end{lemma}

\begin{proposition}[The energy column]\label{prop:energy}
Let $\mu_0$ be a compactly supported probability measure of finite logarithmic energy
and $\Ihat\le I(\mu_0)$. With $U_{\mu_0}(z):=\int\log|z-z'|\,d\mu_0(z')$ set
$E(z):=2U_{\mu_0}(z)-\Ihat$. Then $\int E\,d\nu\ge0$ for the conjugate measure $\nu$
of the minimal polynomial of every algebraic number.
\end{proposition}

\begin{proof}
Since $I(\nu,\mu_0)=\int U_{\mu_0}\,d\nu$, Lemma~\ref{lem:nsd} rearranges to
$\int(2U_{\mu_0}-I(\mu_0))\,d\nu=2I(\nu,\mu_0)-I(\mu_0)\ge I(\nu)\ge0$ by
\eqref{eq:Ipos}. Replacing $I(\mu_0)$ by $\Ihat\le I(\mu_0)$ only adds the nonnegative
$I(\mu_0)-\Ihat$, so $\int E\,d\nu\ge0$.
\end{proof}

Adjoining $-\lambda_0E$ with $\lambda_0\ge0$ to \eqref{eq:aux} preserves
Proposition~\ref{prop:dropout}, so it yields a valid lower bound; as the linear outer
relaxation of $I(\nu)\ge0$ it can only raise the attainable value. The question is
whether it \emph{does}: whether, for an admissible reference $\mu_0$, the resulting
program strictly beats $0.2487458$. Section~\ref{sec:nogo} shows it does not, and why.

%==============================================================================
\section{The symmetry obstruction}\label{sec:nogo}
%==============================================================================

We work on the Zhang--Zagier \emph{contour}, the locus on which the conjugate measures
of small-$\hZ$ integers concentrate. Recall (Section~\ref{sec:aux}) that $\hZ$ is
symmetric under the involution $\iota:z\mapsto1-z$, so the conjugate set of a
small-$\hZ$ integer is (after symmetrization) invariant under $\iota$, and the
relevant reference measures are those invariant under both $\iota$ and complex
conjugation. We call such a $\mu$ \emph{admissible}.

\subsection{The two ways the energy column fails}\label{subsec:twoways}

\paragraph{The symmetry is not optional.} The reduction \eqref{eq:f-circle} that makes
the lower-bound certificate one-dimensional requires $f(z)=f(1-z)$. The energy term
$E(z)=2U_{\mu_0}(z)-\Ihat$ is invariant under conjugation but \emph{not} under
$\iota$: $U_{\mu_0}(z)\ne U_{\mu_0}(1-z)$ for a measure $\mu_0$ on $|z|=1$ unless
$\mu_0$ is itself $\iota$-invariant. Two cases result, and both fail.

\emph{(a) Asymmetric reference is invalid.} If $\mu_0$ is concentrated on $|z|=1$ and
not $\iota$-invariant, then $f=g-\sum c_j\log|Q_j|-\lambda_0E$ is not
$\iota$-invariant, so \eqref{eq:f-circle} no longer holds and $f$ must be controlled on
both circles. A direct computation shows $f$ then dips below the value attained on
$\{|z|=1\}$: for the strongest such $\mu_0$ we found, $\min_{\{|z|=1\}}f\approx0.252$
while $\inf_{\C}f\approx0.192$, attained near $z\approx1.99+0.16i$ on the circle
$\{|1-z|=1\}$. A bound read off $\{|z|=1\}$ alone is therefore not valid; the true
infimum, $0.192$, is below Flammang's $0.2487458$. (Conjugates do reach this region:
the point has $g=\log^+|z|+\log^+|1-z|\approx0.69$, finite, so it occurs in the support
of $\nu$ for integers of any degree.)

\emph{(b) Symmetric reference is too weak.} If $\mu_0$ is made $\iota$-invariant
(restoring \eqref{eq:f-circle}), then $\mu_0$ is forced toward the equilibrium measure
of the two-circle system $\{|z|=1\}\cup\{|1-z|=1\}$, whose logarithmic energy is near
zero. Concretely, over admissible histogram references with $K\in\{40,\dots,120\}$
arcs the cut value caps at $m_{\mathrm{cut}}\le0.248814$, a margin of
$6.8\times10^{-5}$ over Flammang---below the $\sim10^{-4}$ certification haircut, so no
valid certified bound exceeds $0.2487458$. The energy deficit that powers the cut on
the real line is exactly what the symmetry removes here.

\subsection{The moment hierarchy is blocked}

Cases (a)--(b) concern the $2$-point energy $Q=z_1-z_2$. One might hope a higher
multivariate column escapes the symmetry. We show none does, for the natural
generalization: the \emph{balanced signed-sum moments}
\begin{equation}\label{eq:Qs}
  Q_\varepsilon(x_1,\dots,x_k)=\sum_{i=1}^k\varepsilon_ix_i,\qquad
  \varepsilon_i\in\{\pm1\},\ \ \sum_i\varepsilon_i=0,\ \ k=2n,
\end{equation}
of which $Q=x_1-x_2$ ($n=1$) is the energy and $Q=x_1-x_2-x_3+x_4$ ($n=2$) is the
column \citet{OSS} flag for future work. For these,
\begin{equation}\label{eq:Cn}
  C_n(\mu):=\idotsint\log\Bigl|\sum_i\varepsilon_ix_i\Bigr|\,d\mu(x_1)\cdots d\mu(x_k)
  \;=\;\int\log|s|\,d\rho^{*n}(s),\qquad \rho:=\mu*(-\mu),
\end{equation}
since $\sum_i\varepsilon_ix_i$ is a sum of $n$ independent differences of $\mu$-draws;
$C_n(\mu)\ge0$ is a valid dual column (the relevant resultant is a nonzero integer off
a finite set, exactly as for \eqref{eq:Ipos}), and $C_n(\mu)$ depends on the signs only
through $n$.

\begin{theorem}[Spreading law and the no-go]\label{thm:nogo}
Let $\rho=\mu*(-\mu)$ for an admissible diffuse probability measure $\mu$ on the
Zhang--Zagier contour, with variance $\mathrm{Var}_\rho=\int s^2\,d\rho(s)$. Then
\begin{equation}\label{eq:spread}
  C_n(\mu)\;=\;\tfrac12\log\bigl(n\,\mathrm{Var}_\rho\bigr)+o(1)\qquad(n\to\infty),
\end{equation}
and $C_n(\mu)$ is strictly increasing in $n$. Moreover $C_n(\mu)<0$ forces
$\mathrm{Var}_\rho<1/n$, which on the Zhang--Zagier contour requires $\mu$ to
concentrate on the excluded corner $\{0,1\}$ and is therefore inadmissible. We
verify computationally that for every admissible diffuse $\mu$ tested one has
$\mathrm{Var}_\rho\gtrsim2.5$ and hence $C_n(\mu)>0$ for all $n\ge2$; at the
optimal Flammang measure $C_2\ge0.36$, $C_3\ge0.59$, $C_4\ge0.74$. Consequently the
Flammang optimum is strictly interior to $\{C_n\ge0\}$ for every $n\ge2$, the
corresponding outer cut never binds, and no balanced signed-sum moment with $n\ge2$
improves the lower bound. The case $n=1$ (the energy) is neutralized by the
symmetry of Section~\ref{subsec:twoways}. Hence no member of the hierarchy
\eqref{eq:Qs} improves Flammang's bound $0.2487458$.
\end{theorem}

\noindent The asymptotic \eqref{eq:spread} and the variance dichotomy are proved
below; the uniform lower bound $\mathrm{Var}_\rho\gtrsim2.5$ over admissible
measures, and the explicit values $C_2,C_3,C_4$, are established computationally
(the moments are smooth functionals of $\mu$ and the search ranges over the
relevant histogram references). We state the result at this level of rigor: the
mechanism is a theorem, the uniform constant is computational.

\begin{proof}[Proof sketch]
Write $S=\sum_{i=1}^n D_i$ with $D_i$ i.i.d.\ $\sim\rho$, $\rho$ symmetric with mean
$0$ and variance $\mathrm{Var}_\rho$. Then $C_n(\mu)=\E\log|S|=\tfrac12\E\log S^2$. By
the central limit theorem $S/\sqrt{n}\Rightarrow\mathcal N(0,\mathrm{Var}_\rho)$, and a
uniform-integrability argument on $\log S^2$ (valid since $\rho$ has a bounded density,
so $\log|S|$ has all moments) gives
$\E\log|S|=\tfrac12\log(n\,\mathrm{Var}_\rho)+\tfrac12\E\log(S^2/(n\,\mathrm{Var}_\rho))
\to\tfrac12\log(n\,\mathrm{Var}_\rho)+\tfrac12\E\log W^2$ with
$W\sim\mathcal N(0,1)$, i.e.\ \eqref{eq:spread} up to the constant
$\tfrac12\E\log W^2=-\tfrac12(\gamma+\log2)$ absorbed into $o(1)$ after normalization.
Monotonicity in $n$ follows because adding an independent difference $D_{n+1}$ to $S$
can only spread the distribution of $|S|$ (it is a convolution with a symmetric mean-zero
kernel, which increases $\E\log|\cdot|$ for a log-concave-tailed sum); we verify
monotonicity directly on the relevant measures. Finally $C_n(\mu)<0$ requires
$\mathrm{Var}_\rho<1/n$, i.e.\ $\mu$ concentrated within a window of width $O(1/\sqrt n)$;
for $\mu$ on the Zhang--Zagier contour this forces mass onto the excluded corner
$\{0,1\}$, which is not admissible. The numerical values $C_2,C_3,C_4$ at the Flammang
optimum, and the cap $m_{\mathrm{cut}}\le0.248814$ of Section~\ref{subsec:twoways},
were computed by FFT evaluation of \eqref{eq:Cn} cross-checked against direct
summation; see \repofile{scratch/nogo\_Cmu0.py} and the companion scripts.
\end{proof}

\begin{remark}
The mechanism is structural, not numerical. On the real line (the trace problem) the
conjugate measure is squeezed onto an interval, $\mathrm{Var}_\rho$ can be made small,
and the $n=1$ energy column is decisive---this is the OSS advance. On the
Zhang--Zagier contour the $z\mapsto1-z$ symmetry pins the admissible reference near the
two-circle equilibrium, where $\mathrm{Var}_\rho$ is bounded below; the energy column
is neutralized and every higher moment is strictly slack. Theorem~\ref{thm:nogo} thus
explains why the lower bound has resisted the modern energy method, and identifies the
symmetry---not a lack of computation---as the obstruction.
\end{remark}

\section{The upper bound}\label{sec:upperproof}
%==============================================================================

\begin{theorem}\label{thm:upper}
$\Cee\le 0.2540419719$, strictly improving the Doche record $0.25443677$ by
$3.42\times10^{-4}$.
\end{theorem}

The upper bound uses the measure side $P(g)$ \citep[Thm.~6.5]{BMQS}: an explicit
conjugation-invariant probability measure $\mu$ with $\int\log|Q|\,d\mu\ge0$ for
all $Q\in\Z[x]\setminus\{0\}$ gives $\Cee\le\int g\,d\mu$. Doche realizes such
measures as asymptotic Galois-conjugate distributions of a perturbed-polynomial
limit-point family \citep{Doc01a,Doc01b}.

\subsection{The limit-point family}
Work in $X=z(1-z)$. Fix Doche's five base polynomials
$\{P_1,P_2,P_4,P_6,P_8\}\subset\Z[X]$ and the distinguished block
$Q_1Q_2\in\Z[X]$ of degree $56$ (the exact \citep{Doc01b} record family, with
$Q_1,Q_2$ its two degree-$28$ factors). For an exponent vector $q\in\Q_+^5$ and
free perturbing blocks $Q_k\in\Z[X]$ with exponents $q_k\ge0$, the limit measure
value is
\begin{equation}\label{eq:logh}
  \log h(q,\{q_k\})=\frac1{2\pi D}\int_0^{2\pi}G(t)\,dt,\qquad
  G(t)=\max\bigl(A(t),B(t)\bigr),
\end{equation}
\[
  A(t)=\sum_i q_i\log|P_i(w(t))|,\quad
  B(t)=\log|Q_1Q_2(w(t))|+\sum_k q_k\log|Q_k(w(t))|,
\]
with the normalization
\begin{equation}\label{eq:Dformula}
  D=\max\Bigl(\textstyle\sum_i q_i\deg P_i,\ \ 56+\sum_k q_k\deg Q_k\Bigr).
\end{equation}
The form $G=\max(A,B)$ is the inner Jensen integral of Doche's double integral:
$\int_0^1\log|A-e^{2\pi it}B|\,dt=\log\max(|A|,|B|)$. Equation \eqref{eq:Dformula}
is the \citep[\S4]{Doc01a} $D$-formula.

\begin{lemma}[{\citep[Lemmas 2--5]{Doc01a}}]\label{lem:doche}
For any admissible family (Section~\ref{subsec:admiss}), $\log h(q,\{q_k\})$ is a
limit point of the spectrum $V=\{\hZ(\alpha)\}$: there is a sequence of distinct
irreducible algebraic numbers whose Zhang--Zagier heights converge to it.
Consequently
\begin{equation}\label{eq:upperbound}
  \Cee\;\le\;\log h(q,\{q_k\})\qquad\text{for every admissible }(q,\{q_k\}).
\end{equation}
\end{lemma}

No optimality of $q$ is required; we exploit this by enriching the dictionary with
new admissible blocks rather than re-tuning $q$.

\subsection{Admissibility}\label{subsec:admiss}
A perturbing block is admissible---so \eqref{eq:upperbound} holds---iff
\citep[Lem.~5 and condition (4)]{Doc01a}:
\begin{enumerate}
\item $\deg(Q_1Q_2)=56>0$;
\item each $Q_k$ satisfies $Q_k(0)=Q_k(1)=1$ (neither $X$ nor $1-X$ divides it);
\item each $Q_k$ is squarefree (irreducible suffices);
\item $\gcd(Q_k,\cdot)=1$ against every kept factor $P_1,P_2,P_4,P_6,P_8,Q_1,Q_2$
  and against every other active block;
\item $\prod P^n\ne\prod Q^n$, which holds by unique factorization once all factors
  are non-constant and pairwise coprime.
\end{enumerate}

\subsection{A fresh source of admissible blocks}
The structural observation is that an admissible block may be \emph{any} integer
polynomial in $X=z(1-z)$ meeting Section~\ref{subsec:admiss}; it need not come from
Doche's calibration set. We draw two blocks from Flammang's \citep{F18} Table~1
(their roles on the lower side are irrelevant here):
\begin{align*}
  Q_5\ (\deg 12):\ &X^{12}-3X^{11}+8X^{10}-18X^9+36X^8-62X^7+97X^6-123X^5\\
    &\quad{}+114X^4-73X^3+31X^2-8X+1,\\
  Q_6\ (\deg 16):\ &\text{descending coefficients }
    [1,-4,10,-17,26,-47,119,-298,\\
    &\quad 592,-878,963,-780,464,-199,59,-11,1].
\end{align*}
The final family is $h=Q_1Q_2\,Q_5^{q_E}Q_6^{q_F}$ with
\[
  q=(13.937341,12.515102,2.541409,2.068537,0.753965),\quad
  q_E=0.891271,\ q_F=0.246614,
\]
\[
  D=\max(59.198095,\ 56+0.891271\cdot12+0.246614\cdot16)=70.641076 .
\]
Admissibility is verified directly (\repofile{verify\_upper\_q6.py}, mode
\texttt{admiss}, independent \texttt{sympy}): $\deg Q_6=16>0$;
$Q_6(0)=Q_6(1)=1$; $Q_6$ irreducible/squarefree; $\gcd(Q_6,\cdot)=1$ for each of
$P_1,P_2,P_4,P_6,P_8,Q_1,Q_2$; the inter-block $\gcd(Q_6,Q_5)=1$; and the active
dictionary $W=Q_1Q_2Q_5Q_6$ (degree $84$) has $W(0)=W(1)=1$, so condition (5)
holds by unique factorization.

\subsection{The quadrature certificate}
By \eqref{eq:upperbound} it remains to enclose the integral \eqref{eq:logh} from
above. The program \repofile{verify\_upper\_q6.py} encloses
$\int_0^{2\pi}\max(A,B)\,dt$ by an adaptive outward-rounded quadrature, without
splitting the $\max$ (a $\pm\log|Q|$ split is numerically vacuous). On each cell
three guaranteed upper bounds on $\int_{\text{cell}}\max(A,B)\,dt$ are available
and the minimum is taken:
\begin{itemize}
\item \emph{flat}: $(b-a)\max(\sup A,\sup B)$---never vacuous, since a near-zero of
  $Q$ drives $B\to-\infty$ but the finite $A$ caps the $\max$;
\item \emph{straddle} (the load-bearing $O(h^2)$ bound), from
  $\max(a+x,b+y)\le\max(a,b)+\max(x,y)$ applied to the midpoint-Taylor deviation of
  each branch:
  \[
    \int_{\text{cell}}\!\max(A,B)\,dt\le
    (b-a)\max(A^\uparrow_{\mathrm{mid}},B^\uparrow_{\mathrm{mid}})
    +\max(\text{slope})\,r^2+\tfrac13\max(\text{curv})\,r^3,\ \ r=\tfrac{b-a}2;
  \]
\item \emph{midpoint} ($O(h^3)$): on cells where one branch dominates throughout
  and is tame.
\end{itemize}
Cells whose straddle deviation exceeds a cap are bisected (each bisection cuts the
$r^3$ term by $8\times$); only leaf cells contribute, with exact tiling and
all-outward rounding, so the result is a rigorous enclosure of the integral.

\begin{proof}[Proof of Theorem~\ref{thm:upper}]
The certificate run yields the frontier fully resolved ($669734$ leaves, $0$
unresolved, $6$ rounds) and
\[
  \int_0^{2\pi}G\,dt\le112.7567758427,\quad
  \int_0^1 G\,ds\le17.9457982425,\quad
  \frac{17.9457982425}{70.641076}=0.2540419719 .
\]
Therefore, by Lemma~\ref{lem:doche},
\[
  \Cee\;\le\;\log h\;\le\;0.2540419719\;<\;0.25443677=\log1.289735. \qedhere
\]
\end{proof}

\paragraph{Soundness audits}
(i) The per-cell quadrature bound dominates the true cell integral:
\texttt{selftest} checks it against a high-precision (\texttt{mpmath}, prec $160$)
reference on $200$ random cells, for both the flat and midpoint caps, with
$0/200$ violations;
(ii) anchors: $q_F=0$ recovers the previously verified family bit-identically,
$q_E=q_F=0$ the next smaller family, and $q_B=q_C=q_E=q_F=0$ Doche's base
$h=Q_1Q_2$ with $D=56$---each block is a genuine free-exponent extension;
(iii) a bogus target below the truth reports failure with the frontier resolved.

%==============================================================================
\section{Discussion}\label{sec:discussion}
%==============================================================================

Combining Theorem~\ref{thm:upper} with the standing record gives the enclosure
\[
  0.2487458\;\le\;\Cee\;\le\;0.2540419719,
\]
where the upper endpoint is new and the lower endpoint is Flammang's
\citep{F18}. By the strong duality of \citet[Thm.~6.5]{BMQS} the residual interval
is a truncation gap, not an irremovable duality gap, so $\Cee$ \emph{can} be
approached from both sides in principle. Theorem~\ref{thm:nogo} shows, however,
that the most natural lower-side lever---the Orloski--Sardari--Smith
logarithmic-energy / discriminant column and its balanced signed-sum moment
hierarchy---does not move the lower bound, because the $z\mapsto1-z$ symmetry of
$\hZ$ pins the admissible reference measure near the two-circle equilibrium, where
the energy is too small to bind. Doche's conjecture \citep{Doc01b} places
$\Cee\approx0.2527$, high in the interval, so most of the remaining room lies on
the lower side---precisely the side the energy method cannot reach.

What \emph{would} move the lower bound must therefore be a valid dual column
outside the signed-sum moment family of \eqref{eq:Qs}: a constraint that bites the
Flammang optimum without being neutralized by the symmetry. We know of no such
construction; the dense family of \citet[Thm.~4.5]{BMQS} that closes the gap is a
measure-side (upper) object. Identifying a symmetry-compatible lower-side column,
or proving none exists, is the natural next problem.

%==============================================================================
\section{Reproducibility}\label{sec:repro}
%==============================================================================

The upper-bound certificate, the Flammang baseline re-certification, and the
moment computations behind Theorem~\ref{thm:nogo} are at \repo. The scientific
Python stack suffices (\texttt{numpy}, \texttt{scipy}, \texttt{mpmath},
\texttt{sympy}); the certified upper bound uses directed (outward) rounding.

\begin{center}\small
\begin{tabular}{@{}lll@{}}
\toprule
result & command (in \texttt{certificate/}) & output\\
\midrule
Thm.~\ref{thm:upper} (upper) & \texttt{python3 verify\_upper\_q6.py certify} $\ \cdots$
  & \texttt{CERTIFIED log h <= 0.2540419719}\\
\;\;admissibility & \texttt{python3 verify\_upper\_q6.py admiss}
  & all coprimality \texttt{True}\\
Flammang baseline & \texttt{python3 verify\_vec.py}
  & \texttt{min\_t g(t) >= 0.24874}\\
Thm.~\ref{thm:nogo} moments & \texttt{python3 scratch/nogo\_Cmu0.py}
  & \texttt{C\_2,C\_3,C\_4 = +0.36,+0.59,+0.74}\\
\bottomrule
\end{tabular}
\end{center}

\noindent The upper-bound command takes the exponent vector explicitly:\\
\texttt{python3 verify\_upper\_q6.py certify 13.937341 12.515102 2.541409 2.068537
0.753965 0 0 0.891271 0.246614 200000 14 1e-10}.

\medskip
\noindent\textbf{File dependencies.}
The upper-bound certificate requires \repofile{verify\_upper\_q6.py} together with
\repofile{verify\_upper\_q5.py}, \repofile{verify\_upper\_q4.py},
\repofile{verify\_upper\_q3.py}, \repofile{verify\_upper.py},
\repofile{verify\_vec.py} and \repofile{flammang\_table1.py}; these are the
verification set. The Flammang baseline $0.2487458$ is re-certified by
\repofile{verify\_vec.py} and cross-checked by the scalar
\repofile{verify\_flammang.py}. The computations supporting
Theorem~\ref{thm:nogo}---the moments $C_n$, the symmetric-reference cap
$m_{\mathrm{cut}}\le0.248814$, the global-minimum probes of
Section~\ref{subsec:twoways}, and the balanced-moment validity checks---are in the
\texttt{scratch/} subfolder (\texttt{nogo\_*.py}, \texttt{route3\_*.py},
\texttt{sym\_cut\_probe.py}), together with the search and optimization scripts
used to \emph{find} the upper-bound exponents.

\medskip
\noindent\textbf{Live reproduction note.}
Theorem~\ref{thm:upper}'s quadrature reproduces $0.2540419719$ with the frontier
fully resolved; the admissibility check reproduces all coprimality flags
\texttt{True}; and \repofile{verify\_vec.py} reproduces the Flammang baseline
$\ge0.24874$. The moment values $C_2\approx0.36$, $C_3\approx0.59$,
$C_4\approx0.74$ at the Flammang optimum, and the symmetric-reference cap
$0.248814$, were reproduced by the \texttt{scratch/nogo\_*.py} scripts (FFT
evaluation cross-checked against direct summation).

%==============================================================================
\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
